Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-29 latex/comp_or.tex
Comp OR paper update

	\item All items allocated on a pallet must have the same destination. A pallet which has not yet reached its destination may receive more items, although it is known that these operations of removing restraining nets increase handling time and the risk of improper delivery. We do not consider over-sized cargo in this work, but only cargoes that fit on these pallets.

@@

\bgroup
\def\arraystretch{1.2}
\begin{table}[H]
	\centering
	\small
	\begin{tabular}{MT}
		&Informally, ACLP+RPDP can be summarized as follows:\\
		\midrule
		max &  (items score sum) / (tour cost) of picked up and delivered items on a tour  \\
		\midrule
s.t.    & Along a tour, the set of unvisited nodes is updated. \\
		& In each node, an item may be included in at most one pallet.\\		
		& In each node, consolidated items are composed of items with the same destination. \\
		& Weight, volume and score of a consolidated item are the corresponding sum of their components.\\
		& Consolidated items remain on board until their destinations.\\	
		& Consolidated items can only be included in the same pallet if their destinations are the same.\\
		& Only items destined for the remaining nodes can be loaded.  \\
		& The lateral and longitudinal torques must be within the operational range of the aircraft.\\
		& Weight and volume limitations of pallets must be respected.\\
		& The total weight must be less than the aircraft payload or the total pallet capacity, whichever is the lowest.\\	
		& {\bf The pallets destined for the next node of the tour should be put as near as possible to the cargo ramp door (our inclusion)}.\\
		& {\bf The items allocated to each pallet should be submitted to a 3D packing procedure (our inclusion)}.\\				
		\midrule
	\end{tabular}
	\normalsize
\end{table}
\egroup

@@

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets Greedy(p_i,\ N^{\pi_k},\ \pi(k),\ nodeTorque,\ G,\ limit,\ lock,\ ts )$   \label{mpShims:greedy}
		\State $proc_i.start$
		\EndFor

@@

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets getBestShims(p_i,\ N^{\pi_k},\ \pi(k),\ nodeTorque,\ G,\ surplus,\ lock,\ ts )$ \label{mpShims:getBestShims}
		\State $proc_i.start$
		\EndFor

@@

Let $n^i$ be the number of items assigned to pallet $i$ and $m$ the number of pallets.

@@

Let $X_{ij} = 1$ if item $j$ was already assigned to pallet $i$ by {\it mpShims}, $X_{ij}\ =\ 0$ otherwise.

@@

Algorithm \ref{alg:3dpacking} presents the multiprocessing solution method for 3D packing to be applied after {\it mpShims}, to guarantee that the item to be palletized actually fit into the pallet.

@@

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets 3Dpacker(p_i,\ N^{\pi_k}_i,\ \pi(k),\ G )$   \label{3dpacking:3}
		\State $proc_i.start$
		\EndFor

@@

According to line \ref{3dpacking:1}, this method receives an initial solution produced by {\it mpShims}, and according to line \ref{3dpacking:2}, each pallet has its own process.

@@

As in the larger aircraft the number of pallets is bigger than the number of threads available in a common handheld computer, for parallelization, we used the {\it Python Multiprocessing} package, which implements {\it process-based parallelism} or {\it parallel shared memory algorithm}. According to \cite{multiprocessing}, {\it Multiprocessing} is a package that supports spawning processes using an API similar to the {\it Python Threading} package.

@@

\vspace{2.0mm}
\begin{table}[H]
	\centering
	\caption{Volume surpluses, methods and scenarios results {\bf after} 3D packing}  \label{tab:results2}
	\footnotesize
	\begin{tabular}{crcccccccc}
		\toprule
		{\bf Volume}     &{\bf Resolution}&                    &\multicolumn{6}{c}{\bf Scenarios}                                                   &{\bf Normalized}\\
		\cmidrule{4-9}		
		{\it surplus}    &{\it method}    & {\bf Results}      &{\bf 1}    &{\bf 2}    &{\bf 3}    &{\bf 4}    &{\bf 5}    &{\bf 6}    &{\bf Speedup} \\
		\toprule
		\multirow{7}{*}{$1.2$}&$Relaxed$  & $f$                &   11.47   &    7.24   &{\bf 10.78}&     12.06 &     12.97 &    12.44  &     0.95 \\%
		&                       $MIP$     & {\it run time (s)} &     12     &     51    &     81    &     258   &      601  &     3161  &{\bf 1.15}\\% 	4164				
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &    9.05   &   5.11    &   9.75    &   10.96   &   12.86   &   13.25   &     0.86 \\% 
		&                                 & {\it run time (s)} &     16    &     68    &     94    &    323    &    719    &    3549   &     1.00 \\% 	4769		
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 12.14}&{\bf 7.29} &   10.36   &{\bf 12.63}&{\bf 14.04}&{\bf 13.92}&{\bf 0.99}\\% best 7080
		&                                 & {\it run time (s)} &     9     &     36    &     54    &     192   &     427   &    2118   &{\bf 1.70}\\%	2836	
		\toprule		
		\multirow{7}{*}{$1.5$}&$Relaxed$  & $f$                &     15.83 &{\bf 10.08}&{\bf 15.14}&{\bf 16.87}&     18.58 &     17.52 &     0.97 \\%  
		&                      $MIP$      & {\it run time (s)} &    20     &     83    &     142   &     362   &     996   &     4741  &{\bf 1.22} \\% 6344					
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &   11.55   &   7.61    &   12.28   &   15.00   &   17.55   &   17.57   &     0.84  \\%  
		&                                 & {\it run time (s)} &    25     &    107    &     156   &    498    &    1217   &   5743    &     1.00  \\% 7746
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 17.05}&   10.01   &   15.01   &   16.75   &{\bf 20.09}&{\bf 17.85}&{\bf 1.00} \\%   best 9708
		&                                 & {\it run time (s)} &    18     &    64     &     101   &    351    &   828     &  3879     &     1.50  \\% 5421
		\toprule
		\multirow{7}{*}{$2.0$}&$Relaxed$  & $f$                &     23.73 &{\bf 15.23}&   21.96   &   24.22   &   26.69   &    24.29  &     0.99  \\%  
		&                       $MIP$     & {\it run time (s)} &    28     &     99    &     185   &    648    &   1680    &   8774    &     1.00  \\% 11414					
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}        & $f$                &   16.28   &   10.93   &   18.16   &   22.35   &   25.12   &   24.53   &     0.85  \\%  
		&                                 & {\it run time (s)} &    37     &    141    &   196     &     653   &   1453    &   6851    &     1.22  \\% 9331
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}      & $f$                &{\bf 24.52}&   15.18   &{\bf 21.99}&{\bf 24.61}&{\bf 26.94}&{\bf 24.83}&{\bf 1.00} \\% best 13812
		&                                 & {\it run time (s)} &    27     &    87     &   146     &    496    &   1080    &   5160    &     1.63  \\% 6996
		\bottomrule	
	\end{tabular}
	\normalsize
\end{table}

@@

(3) The procedure for 3D packing generated an unfit item rate of, on average, 17\% after {\it Shims} solutions, 13\% after {\it mpShims} solutions, and 9\% after the MIP solver solutions. 
We are conscious that this unfit rate could be smaller if we had chosen \cite{PaquayLimbourgSchynsOliveira2018} approach, but as we are concerned with an operational application where the running time is crucial, we stick to faster approximate approaches like the {\it First Fit Decreasing} (first orientation that fits) and the {\it Best Fit} (best pivot point if more than one is available).

>>>>

	\item All items allocated on a pallet must have the same destination. A pallet which has not yet reached its destination may receive more items, although it is known that these operations of removing restraining nets increase handling time and the risk of improper delivery.

	\item We do not consider over-sized cargo in this work, but only cargoes that fit on these pallets.

@@

\bgroup
\def\arraystretch{1.2}
\begin{table}[H]
	\centering
	\small
	\begin{tabular}{MT}
		&Informally, ACLP+RPDP can be summarized as follows:\\
		\midrule
		max &  (items score sum) / (tour cost) of picked up and delivered items on a tour  \\
		\midrule
\multicolumn{2}{l}{--- from \cite{MesquitaSanches2023} ---}\\		
s.t.    & Along a tour, the set of unvisited nodes is updated. \\
		& In each node, an item may be included in at most one pallet.\\		
		& In each node, consolidated items are composed of items with the same destination. \\
		& Weight, volume and score of a consolidated item are the corresponding sum of their components.\\
		& Consolidated items remain on board until their destinations.\\	
		& Consolidated items can only be included in the same pallet if their destinations are the same.\\
		& Only items destined for the remaining nodes can be loaded.  \\
		& The lateral and longitudinal torques must be within the operational range of the aircraft.\\
		& Weight and volume limitations of pallets must be respected.\\
		& The total weight must be less than the aircraft payload or the total pallet capacity, whichever is the lowest.\\
\multicolumn{2}{l}{--- our inclusion ---}\\
s.t.    & Pallets destined for the next node should be put as near as possible to the ramp door.\\
		& Items allocated to the pallet must fit on the pallet before consolidation.\\				
		\midrule
	\end{tabular}
	\normalsize
\end{table}
\egroup

@@

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets Greedy(p_i,\ N^{\pi_k},\ \pi(k),\ nodeTorque,\ G,\ limit,\ lock,\ ts )$   \label{mpShims:greedy}
		\State $proc_i.fork$
		\EndFor

@@

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets getBestShims(p_i,\ N^{\pi_k},\ \pi(k),\ nodeTorque,\ G,\ surplus,\ lock,\ ts )$ \label{mpShims:getBestShims}
		\State $proc_i.fork$
		\EndFor

@@

The algorithm $3Dpacker$ is implemented according to the mathematical model that follows:

Let $n^i$ be the number of items assigned to pallet $i$ and $m$ the amount of pallets.

@@

Let $X_{ij} = 1$ if item $j$ was already assigned to pallet $i$ by the previous resolution, $X_{ij}\ =\ 0$ otherwise.

@@

Algorithm \ref{alg:3dpacking} presents the multiprocessing solution method for 3D packing to be applied to an existent solution, to guarantee that the item to be palletized actually fit into the pallet.

@@

		\For{$i \gets 1$ to $m$}
		\State $proc_i \gets 3Dpacker(p_i,\ N^{\pi_k}_i,\ \pi(k),\ G )$   \label{3dpacking:3}
		\State $proc_i.fork$ \Comment{pallet $p_i$ packing processes is forked}
		\EndFor

@@

According to line \ref{3dpacking:1}, this method receives an initial solution produced by a previous resolution, and according to line \ref{3dpacking:2}, each pallet has its own process.

@@

As in the larger aircraft the number of pallets is bigger than the number of threads available in a common handheld computer, for parallelization, we used the {\it Python Multiprocessing} package, which implements {\it process-based parallelism} or {\it parallel shared memory algorithm}. More details on {\it process-based parallelism} may be found in  \cite{multiprocessing}.

@@

\vspace{2.0mm}
\begin{table}[H]
	\centering
	\caption{Volume surpluses, methods and scenarios results {\bf after} 3D packing (3Dp)}  \label{tab:results2}
	\footnotesize
	\begin{tabular}{crcccccccc}
		\toprule
		{\bf Volume}     &{\bf Resolution}&                    &\multicolumn{6}{c}{\bf Scenarios}                                                   &{\bf Normalized}\\
		\cmidrule{4-9}		
		{\it surplus}    &{\it method}    & {\bf Results}      &{\bf 1}    &{\bf 2}    &{\bf 3}    &{\bf 4}    &{\bf 5}    &{\bf 6}    &{\bf Speedup} \\
		\toprule
		\multirow{7}{*}{$1.2$}&$Relaxed$  & $f$                &   11.47   &    7.24   &{\bf 10.78}&     12.06 &     12.97 &    12.44  &     0.95 \\%
		&                       $MIP+3Dp$     & {\it run time (s)} &     12     &     51    &     81    &     258   &      601  &     3161  &{\bf 1.15}\\% 	4164				
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims+3Dp$}        & $f$                &    9.05   &   5.11    &   9.75    &   10.96   &   12.86   &   13.25   &     0.86 \\% 
		&                                 & {\it run time (s)} &     16    &     68    &     94    &    323    &    719    &    3549   &     1.00 \\% 	4769		
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims+3Dp$}      & $f$                &{\bf 12.14}&{\bf 7.29} &   10.36   &{\bf 12.63}&{\bf 14.04}&{\bf 13.92}&{\bf 0.99}\\% best 7080
		&                                 & {\it run time (s)} &     9     &     36    &     54    &     192   &     427   &    2118   &{\bf 1.70}\\%	2836	
		\toprule		
		\multirow{7}{*}{$1.5$}&$Relaxed$  & $f$                &     15.83 &{\bf 10.08}&{\bf 15.14}&{\bf 16.87}&     18.58 &     17.52 &     0.97 \\%  
		&                      $MIP+3Dp$      & {\it run time (s)} &    20     &     83    &     142   &     362   &     996   &     4741  &{\bf 1.22} \\% 6344					
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims+3Dp$}        & $f$                &   11.55   &   7.61    &   12.28   &   15.00   &   17.55   &   17.57   &     0.84  \\%  
		&                                 & {\it run time (s)} &    25     &    107    &     156   &    498    &    1217   &   5743    &     1.00  \\% 7746
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims+3Dp$}      & $f$                &{\bf 17.05}&   10.01   &   15.01   &   16.75   &{\bf 20.09}&{\bf 17.85}&{\bf 1.00} \\%   best 9708
		&                                 & {\it run time (s)} &    18     &    64     &     101   &    351    &   828     &  3879     &     1.50  \\% 5421
		\toprule
		\multirow{7}{*}{$2.0$}&$Relaxed$  & $f$                &     23.73 &{\bf 15.23}&   21.96   &   24.22   &   26.69   &    24.29  &     0.99  \\%  
		&                       $MIP+3Dp$     & {\it run time (s)} &    28     &     99    &     185   &    648    &   1680    &   8774    &     1.00  \\% 11414					
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims+3Dp$}        & $f$                &   16.28   &   10.93   &   18.16   &   22.35   &   25.12   &   24.53   &     0.85  \\%  
		&                                 & {\it run time (s)} &    37     &    141    &   196     &     653   &   1453    &   6851    &     1.22  \\% 9331
		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims+3Dp$}      & $f$                &{\bf 24.52}&   15.18   &{\bf 21.99}&{\bf 24.61}&{\bf 26.94}&{\bf 24.83}&{\bf 1.00} \\% best 13812
		&                                 & {\it run time (s)} &    27     &    87     &   146     &    496    &   1080    &   5160    &     1.63  \\% 6996
		\bottomrule	
	\end{tabular}
	\normalsize
\end{table}

@@

(3) The procedure for 3D packing generated an unfit item rate of, on average, 13\%. We are conscious that this unfit rate could be smaller if we had chosen \cite{PaquayLimbourgSchynsOliveira2018} approach, but as we are concerned with an operational application where the running time is crucial, we stick to faster approximate approaches like the {\it First Fit Decreasing} (first orientation that fits) and the {\it Best Fit} (best pivot point if more than one is available).
